\dnest~Manual

### 2016-01-18 doc/manual.tex
tabs to spaces
wrap onto next line
Julia instructions in the manual

\section{Implementing models}
\dnest~currently includes three example models: SpikeSlab, StraightLine,
RJObject\_SineWaves, and RJObject\_GalaxyField.
It also contains an empty Template example which you can use
to implement your own models.\\

@@

\subsection{Compiling and running your model}
Assuming you implemented your model in the Template directory, there's not
much else for you to do. The file {\tt main.cpp} already contains all the code
you need to construct a sampler and execute it. If your model involves a data
set, you'll just need to make sure you load the dataset at the beginning
of the {\tt main()} function, before doing anything else.\\

@@

%\subsection{Implementing a model using Julia}
%Experimental support for models implemented in Julia is provided in the
%{\tt Examples/JuliaModel} directory. To use this, follow these steps:

%\begin{enumerate}
%\item Implement your log likelihood in {\tt julia\_model.jl}, as a function
%	called {\tt log\_likelihood} that takes a {\tt Vector::Float64} as an argument
%	and returns a {\tt Float64}. You should assume that the priors for the
%	parameters are independent Uniform(0, 1) distributions. To use
%	a different prior, transform the parameters inside
%	your log likelihood function before moving them.\\
%\item You may add other functions to {\tt julia\_model.jl}, for example to load
%	a dataset to refer to in your log likelihood.\\
%\item Edit the constructor for {\tt MyModel} in {\tt MyModel.cpp} so the parameter
%	vector has the correct length for your problem. The default given value
%	is 20.\\
%\item Open the {\tt Makefile} and make sure the {\tt -L} option passed to
%	{\tt g++} points to the
%	directory on your computer where the Julia shared library (such
%	as {\tt libjulia.so}) is stored. You might also have to configure your
%	system so that it searches for libraries here at runtime, e.g.
%	by running ldconfig as root. The \dnest~library and include files should
%	also be somewhere where the compiler will find them (or you can add them
%	to the {\tt g++} calls in the {\tt Makefile} using {\tt -I} for header
%	files and {\tt -L} for libraries).\\
%\item Open {\tt main.cpp} and edit the first argument to the function
%	{\tt jl\_init\_with\_image} to be the path to the file {\tt sys.so} associated with
%	Julia on your system.\\
%\item Compile by invoking '{\tt make}'.\\
%\item Run the executable! Note: only a single thread can be used, so you might want
%	to use the {\tt OPTIONS} file to have more than one particle. Five is a
%	reasonable default.
%\end{enumerate}

>>>>

\section{Implementing models}
\dnest~currently includes three example models: SpikeSlab, StraightLine,
RJObject\_SineWaves, and RJObject\_GalaxyField.
It also contains an empty Template example (in the Templates/BasicModel
subdirectory) which you can use
to implement your own models.\\

@@

\subsection{Compiling and running your model}
Assuming you implemented your model in the Template directory
(Templates/BasicModel), there's not
much else for you to do. The file {\tt main.cpp} already contains all the code
you need to construct a sampler and execute it. If your model involves a data
set, you'll just need to make sure you load the dataset at the beginning
of the {\tt main()} function, before doing anything else.\\

@@

\subsection{Implementing a model using Julia}
Experimental support for models implemented in Julia is provided in the
Templates/JuliaModel directory. There's a HOWTO file in that directory
with instructions for how to use it.
